%% -*- coding: utf-8; -*-

% Use 'digital' option to enable back references. This option is recommended for digital pdf version
%\documentclass[phd,american,digital]{thesispuc}%english thesis
%\documentclass[mscr,american]{thesispuc}%english dissertation
%\documentclass[phd,brazilian]{thesispuc}%tese em portugês
\documentclass[msc,brazilian]{thesispuc}%disseretação em portuguŝ


%%%
%%% Additional Packages
%%%
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage[%
    dvipsnames,
    svgnames,
    x11names,
    fixpdftex,
    table
]{xcolor}
\usepackage{numprint}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{svg}
% ABNT reference style package. The current style is the alphabetical order, if you need
% change to citation order, change in the line above 'alf' to 'num', also at the end replace
% bibliographystyle with the commented version.
\usepackage[num]{abntex2cite}
%\usepackage{tikz}
%\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
%\usepackage{pgfplots,pgfplotstable} 
%\usepackage{array}
\usepackage{longtable}


%% numprint 
\npthousandsep{.}
\npdecimalsign{,}

%% ThesisPUC option
%\tablesmode{fig} %% [nada, fig, tab ou figtab]
%\algoritmsmode{none} %% [none ou use] %% Default is [use]
%\codesmode{none} %% [none ou use] %% Default is [use]
%\abreviationsmode{none} %% [none ou use] %% Default is [use]

\tablesmode{figtab}

\algorithmsmode{none}
\codesmode{none}
\abreviationsmode{use}

% \makeatletter  \renewcommand\@biblabel[1]{#1}  \makeatother

%%%
%%% Counters
%%%

%% uncomment and change for other depth values
\setcounter{tocdepth}{1}
%\setcounter{lofdepth}{3}
%\setcounter{lotdepth}{3}
%\setcounter{secnumdepth}{3}

%%%
%%% Misc.
%%%

\usecolour{true}
%% \graphicspath{ {./figuras/} }
%% https://www.overleaf.com/learn/latex/Inserting_Images
\citebrackets[]

\renewcommand{\arraystretch}{1.5}


%%%
%%% Titulos
%%%

\tituloglossario{Lista de Abreviaturas}
\autor{Antenor Moreira de Barros Leal}
\autorR{Leal, Antenor Moreira de Barros}

\advisor{Adriano Francisco Branco}{Prof.}
\advisorR{Branco, Adriano Francisco}
% If the advisor's department is different from author's department, uncomment the next line and type the correct name and acronym of advisor's institution.
%\advisorInst{institution name}{acronym}

%\coadvisor{Otávio da Fonseca Martins Gomes}{Dr.}
%\coadvisorR{da Fonseca Martins Gomes, Otávio}
%\coadvisorInst{Centro de Tecnologia Mineral}{CETEM/MCTI}

\title{Aplicativo web de auxílio à navegação aérea}
\titleuk{Aerial navigation aid web application}

%%\subtitulo{Aqui vai o subtitulo caso precise}

\day{16}
\month{Junho}
\year{2024}

\city{Rio de Janeiro}
\CDD{004} 
\department{Informática}
\program{\mbox{Engenharia} da \mbox{Computação}}
\school{\mbox{Engenharia} da \mbox{Computação}}
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC-Rio}


%%%
%%% Jury
%%%

\jury{%
  \jurymember{xxxxxxxxxxxxxxxx}{Prof.}
    {Departamento de Informática}{PUC-Rio}
  \jurymember{xxxxxxxxxxxxxxx}{Prof.}
    {Departamento de Informática}{PUC-Rio}
   \jurymember{xxxxxxxxxxxxxxx}{Prof.}
    {Departamento de Informática}{PUC-Rio}
}


%%%
%%% Personal Resume
%%%

\resume{%
% If it fit in one line use this command:
\makebox[\textwidth][s]{Graduando em Engenharia da Computação na PUC - Rio}%
% If not just type your resume without any special command 
}


%%%
%%% Catalog prekeywords
%%%

\catalogprekeywords{%
  \catalogprekey{Informática}%
}

%%%
%%% Keywords - Don't use % at the end of /key dfinition
%%%

\keywords{%
    \key{Aviação}
    \key{Navegação}
    \key{Aplicativo}
    \key{Algoritmo}
    \key{Web}
    \key{Internet}
}

\keywordsuk{%
    \key{Aviation}
    \key{Navigation}
    \key{Application}
    \key{Algoritm}
    \key{Web}
    \key{Internet}
}


%%%
%%% Abstract
%%%

\abstract{%
É um aplicativo web de código aberto com o objetivo de auxiliar usuários de simuladores de voo que não possuem
acesso à ferramenta (Electronic Flight Bag) que um piloto de linha aérea teria. Ao acessar o aplicativo, o usuário
se depara com a lista de aeroportos cadastrados e, após escolher um, são exibidas as informações da pista,
frequências do aeroporto (torre, solo, ATIS, etc.), e frequências de navegação (ILS, VOR, etc.). Também são
apresentadas as informações das condições meteorológicas atuais do aeródromo (vento, visibilidade,
temperatura, etc.), tanto no formato oficial (\abrev METAR), obtidas a cada hora de uma API externa, como em um texto
em linguagem natural para melhor entendimento do jogador iniciante. Um usuário com permissão de
administrador pode adicionar e editar aeroportos. Módulos adicionais estão disponíveis como o cálculo da pista
em uso (a partir de informações do vento) e do perfil de descida.
} 

\abstractuk{%
It is an open source web application to auxialiate the flight simulator's users that don't have
access to the tool (Electronic Flight Bag) that an airline pilot would have. When accessing the app, the users
encounter the list of registered airports and, after choosing one, runway information, airport frequencies 
(tower, ground, ATIS etc) and navigation frequencies (ILS, VOR etc) are showed. Also provided are the current 
meteorological conditions of the aerodrome (wind, visibility, temperature, etc.), both in the official 
format (METAR), obtained hourly from an external API, and in natural language text for better 
understanding by novice players. An administrator user can add and edit airports. Based on the 
current wind information, the active runway is calculated. Additional modules are available such as calculation 
of the runway in use (from wind information) and the descent profile.
}


%%%
%%% Dedication
%%%

% xxxxxxxxxxxxxxxxxxxxxxxx Dedicatória aqui xxxxxxxxxxxxxxxxxxxxxxx
\dedication{%
  
}

%%%
%%% Epigraph
%%%

% epígrafe xxxxxxxxxxxxxxxx
\epigraph{%
 
}
\epigraphauthor{ }
\epigraphbook{ }

%--------------------------------------------
% \usepackage{draftwatermark}

% \SetWatermarkText{{\normalfont SEGUNDA ENTREGA (26/06) rev 1}}

% \SetWatermarkScale{0.2}
% \SetWatermarkAngle{0}
% \SetWatermarkColor{red!80!white}
% \SetWatermarkHorCenter{0.5\paperwidth}
% \SetWatermarkVerCenter{0.1\paperheight}
%--------------------------------------------


\begin{document}
  \input{chapters/1-introducao}
  \input{chapters/2-situacao-atual}
  \input{chapters/3-proposta}
  \input{chapters/3.1-principios-norteadores}
  \input{chapters/4-cronograma}
  \input{chapters/5-metar-decoder}
  \input{chapters/5.1-taf-decoder.tex}
  % \input{chapters/5-vento}
  \input{chapters/6-modelo-dados}
  \input{chapters/7-arquitetura}
  \input{chapters/8-front-end}
  % \input{chapters/9-back-end}
  \input{chapters/99-conclusao}
  \input{chapters/999-apendice-a}

  
  \arial
  \bibliographystyle{abnt-num} % \bibliographystyle{abnt-alf}
  \bibliography{main} 
\end{document}
